\section{FSM and Flowcharts of our robot}{

% \input{asset/flow_chart}

\subsection{Jteson Nano}{
\input{asset/state_transit}
The FSM above illustrate how our robot works. 
\begin{itemize}
    \item 
    Initially, after running the program, the robot will enter the ``IDLE'' mode. In this case, it will stop moving and wait for coming instructions. The program has a GUI allowing users to start and stop the task by clicking buttons. 
    \item 
    When the Start button is pressed, The robot will enter the ``FOLLOW'' mode to follow the black line that is placed beforehand. During the ``FOLLOW'' mode, the robot will also detect the airplane using \lstinline|detectnet|. 
    \item 
    When the robot successfully see the airplane, it will enter the ``CV'' mode. At this state, the robot will  move towards the light source on the landing gear of the airplane. 
    \item 
    When the distance between the airplane and the robot is close enough, the robot will enter the ``GRAB'' mode, the robot arm and the mechanical claw are activated to hold the handle on the airplane. 
    There are in total 4 sensors on the claw with each's NC (normal-close) terminals connected in series, when anyone of them open, the circuit is open and ``IS HOLDING'' flag will become true, which means that the airplane is successfully dragged. 
    \item 
    When IS HOLDING is true, the robot will enter the ``BACK TO LINE'' state to go back to the line by moving backwards. 
    \item 
    As the line tracker at the back of the robot detect the black line, it will enter the ``HOMING'' state to track the line just like the initial ``FOLLOW'' stage, but in reverse direction. There will be a finish sign in the end of the black line such that all the sensor from the line tracker will detect the black color. 
    
\end{itemize}

In this case, the finish flag becomes true. The whole process is finished after the mechanical claw releases  from the airplane and the state goes back to ``IDLE''.
}
}
\subsection{Arduino}{
Chassis Task:
\input{asset/chasis_task_flow_chart}
\newpage
Roboarm Task:
\input{asset/robort_arm_flow_chart}
}
